### 2017-07-19 README.Rmd
Implement success argument in calculate()

---

@@

One categorical (one proportion) (not yet implemented)

```
mtcars %>%
  specify(response = am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "prop")
```

@@

Two numerical vars - SLR  (not yet implemented)

>>>>

---
[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer)

@@

One categorical (one proportion)

```
mtcars %>%
  specify(response = am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "prop", success = "1")
```

@@
